Audio-based multi-level music structure analysis using deep learning

### 2023-01-14 acknowledgements/acknowledgements.tex
Updates from Overleaf

\begin{itemize}
\item I want to express my sincerest gratitude to Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis. Your expertise in MIR helped shape the direction of my research and make it a success. Your unwavering support and encouragement helped me overcome any difficulties I encountered during the process. I also appreciate the time and effort you invested in mentoring me. Your dedication to your students is truly inspiring, and I am honored to have had the opportunity to work with you.
\vspace*{3mm}
\item My co-supervisor
\vspace*{3mm}
\item The Music Technology Group (MTG)
\vspace*{3mm}
\item I would also like to thank my colleague and superior at My Sheet Music Transcriptions, Oriol López, for his exceptional support and flexibility throughout my thesis. His understanding and willingness to accommodate my academic commitments effectively allowed me to balance my work and research responsibilities. His guidance and advice on professional matters have been instrumental in my growth as a professional. I am genuinely grateful for his unwavering support and encouragement and for being a great mentor.
\vspace*{3mm}
Thank you all for being excellent advisors and playing a crucial role in completing my thesis. I sincerely appreciate everything you have done for me and will always cherish the knowledge and experience I have gained under your guidance.
\vspace*{3mm}
\item My family
\vspace*{3mm}
\item My girlfriend
\vspace*{3mm}
\end{itemize}

>>>>

I want to express my sincerest gratitude to...

\begin{itemize}
\item Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis. Your expertise in MIR helped shape the direction of my research and make it a success. Your unwavering support and encouragement helped me overcome any difficulties I encountered during the process. I also appreciate the time and effort you invested in mentoring me. Your dedication to your students is truly inspiring, and I am honored to have had the opportunity to work with you.
\vspace*{3mm}
\item My co-supervisor
\vspace*{3mm}
\item The Music Technology Group (MTG)
\vspace*{3mm}
\item My colleague at My Sheet Music Transcriptions, Oriol López, for his exceptional support and flexibility throughout my thesis. His understanding and willingness to accommodate my academic commitments effectively allowed me to balance my work and research responsibilities. His guidance and advice on professional matters have been instrumental in my growth as a professional. I am genuinely grateful for his unwavering support and encouragement and for being a great mentor.
\vspace*{3mm}
Thank you all for being excellent advisors and playing a crucial role in completing my thesis. I sincerely appreciate everything you have done for me and will always cherish the knowledge and experience I have gained under your guidance.
\vspace*{3mm}
\item My family
\vspace*{3mm}
\item My girlfriend
\vspace*{3mm}
\end{itemize}

### 2023-01-14 introduction/introduction.tex
Updates from Overleaf

MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other fields. It can be applied to various musical styles and genres and has been used for tasks such as music transcription, music generation, and music similarity. \cite{rodriguez2005bilateral}
\section{Motivation}

\section{Objectives}
\section{Structure of the Report}

>>>>

The fundamental concept behind MSA is the ability to divide a song into distinct, non-overlapping segments, assigning a label to each segment that defines its type. This segmentation and labeling process aims to capture a human's perception or analysis of the song.

MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other fields. It can be applied to various musical styles and genres and has been used for tasks such as music transcription, music generation, and music similarity.

\section{Motivation}

In previous work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and performance \cite{Nieto2020}.

\section{Objectives}

\section{Structure of the Report}
